The \dealii{} Library, Version 9.2

### 2020-05-30 9.2/paper.tex
Notes for (future) new additions to code-gallery

\todo[inline]{Do we have new code gallery programs?}

>>>>

\todo[inline]{Do we have new code gallery programs?}
\begin{itemize}
  \item Parallel in time (\url{https://github.com/dealii/code-gallery/pull/49})
  \item Linear elastoplasticity (\url{https://github.com/dealii/code-gallery/pull/62})
  \item Thermo-electro-elastic pump (\url{https://github.com/dealii/code-gallery/pull/63})
  \item Nonlinear poro-viscoelasticity (\url{https://github.com/dealii/code-gallery/pull/72})
\end{itemize}
